An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-07 gas-adsorption/referee-response.md

2. The referee gives a litany of structural properties that we do not address in
   our model: "pore volume, pore size, specific surface area, crystal density,
   skeletal density, packing density, different adsorption sites etc."

We note that some of these (e.g. crystal density, skeletal density) manifestly
have no impact on the property we are studying, which is volumetric storage
capacity.  Others of course do impact the volumetric storage capacity of a
material, but do not relate to an upper bound specifically.

    As discussed in the second and third paragraphs of the results section, our results do put a lower bound of 85% on the void fraction for any porous material that will meet the ARPA-E target for methane volumetric deliverable capacity, and a lower bound of 94% for a material reaching the DOE ULTIMATE target for hydrogen at 298K.  These results *can* guide exploration, if we assume that reaching those targets is the goal.

3. The final suggestion of Referee 1 is that we clearly state the capacity that  
   we report, as discussed by Parilla et al.

@@

Referee 3 states that the conclusions are convincing, and makes two suggestions
for improving the paper:

4. The referee suggests that we attempt to quantify the possible effect of a
   flexible MOF on our upper bound.

We have added a section "Flexible two-phase model" discussing flexible MOFs. We
cannot place a formal upper bound on a flexible MOF in general, but we can put
an upper bound on the capacity of a two-phase MOF such as Co(bdp), if we
constrain the free energy difference between the two phases. This suggests that
this type of a system will require a more stable closed phase in order to reach
the DOE targets.

5. The referee asks that we provide some guidelines in terms of working
   conditions to reach the DOE target.  They further suggest looking at a
   temperature difference to see how that could impact the deliverable capacity.

We added a short explanation of why we cannot apply our upper bound in the case
where the temperature is changed, because a uniform potential may no longer lead
to the optimal deliverable capacity.  Specifically, a non-uniform potential will decrease the entropy of the adsorbed gas, and that decrease will make it easier to desorb the gas by raising the temperature.

### 2021-07-07 gas-adsorption/rsc-gas-ads-complete.tex
add explanation of why non-uniform potential could be good if temperature changes

\startreferees{Added last sentence to clarify why we cannot place a bound
  on the deliverable capacity when the temperature is changed.}

The first limitation of our proof is that we restricted ourselves to
\emph{isothermal} pressure swing storage (which is consistent with the targets set by DOE). By raising the temperature of the
adsorbent during gas discharge to drive off residual
gas~\cite{gomez2014exploring}, the deliverable capacity could be enhanced,
albeit at the cost of a more complicated engineering design of the fuel tank
and vehicle.
%
We cannot place an upper bound on such a process using our approach because with
changing temperature a uniform potential may not give the maximum deliverable
capacity.  \davidsays{As far as I can intuit, \emph{normally} the entropy
increases with temperature, and if that is the case then a uniform potential
will give the optimum deliverable capacity.  If we can prove that for a subset
of substrate interactions (e.g. when the substrate acts as an external potential
felt by the gas), the optimal potential is uniform then we could apply our model
to temperature-pressure swings.}

>>>>

\startreferees{Added an explanation of why we cannot place a bound on the
  deliverable capacity when the temperature is changed.}

The first limitation of our proof is that we restricted ourselves to
\emph{isothermal} pressure swing storage (which is consistent with the targets set by DOE). By raising the temperature of the
adsorbent during gas discharge to drive off residual
gas~\cite{gomez2014exploring}, the deliverable capacity could be enhanced,
albeit at the cost of a more complicated engineering design of the fuel tank
and vehicle.
%
We cannot place an upper bound on such a process using our approach because with
changing temperature a uniform potential may not give the maximum deliverable
capacity.  A nonuniform potential will lower the entropy of the adsorbed gas,
which will make the gas easier to release by raising the temperature.
